A memory frontier for complex synapses: Supplementary material

### 2013-10-01 NIPS/SynapseNIPSsupp.tex
brought NIPS paper down to page limit

% -*- TeX -*- -*- US -*-
\documentclass{article} % For LaTeX2e
\usepackage{nips13submit_e,times}
\input{sl_preamble.tex}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figs/"}}
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%
%additional symbols:
%
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\newcommand{\wv}{\vec{w}}
\newcommand{\wvi}{\vec{w}_\text{ideal}}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distributions
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols for matrices
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{q}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%sets
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
%eigenmodes
\newcommand{\uv}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\CI}{\mathcal{I}}
% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------

@@

A Markov process is described by a matrix of transitions rates, $\MM_{ij}$, from state $i$ to $j$.
The probabilities of being in each state at time $t$, the row-vector $\mathbf{p}(t)$, evolve according to
%
\begin{equation}\label{eq:rowsum}
  \diff{\mathbf{p}(t)}{t} = \mathbf{p}(t) \MM,
  \qquad
  \mathbf{p}(t)\onev=1,
  \qquad
  \MM\onev=0.
\end{equation}
%
In Surya's notes, $\MM=r\frg$.

@@

Which results in our final formula:
%
\begin{equation}\label{eq:SNRcurve}
  \SNR(t) = \sqrt{N} (2f\pot f\dep )\, \eq (\W\pot  - \W\dep )\,\e^{rt\frg}\w.
\end{equation}
%

>>>>

% -*- TeX -*- -*- US -*-
\documentclass{article} % For LaTeX2e
\usepackage{nips13submit_e,times}
\input{sl_preamble.tex}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figs/"}}
% >> Only for drafts! <<
%\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%
%additional symbols:
%
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\newcommand{\wv}{\vec{w}}
\newcommand{\wvi}{\vec{w}_\text{ideal}}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distributions
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols for matrices
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{q}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%sets
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
%eigenmodes
\newcommand{\uv}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\CI}{\mathcal{I}}
% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------

@@

A Markov process is described by a matrix of transitions rates, $\MM_{ij}$, from state $i$ to $j$.
The probabilities of being in each state at time $t$, the row-vector $\mathbf{p}(t)$, evolve according to
%
\begin{equation}\label{eq:rowsum}
  \diff{\mathbf{p}(t)}{t} = \mathbf{p}(t) \MM,
  \qquad
  \mathbf{p}(t)\onev=1,
  \qquad
  \MM\onev=0.
\end{equation}
%

@@

Which results in our final formula:
%
\begin{equation}\label{eq:SNRcurve}
  \SNR(t) = \sqrt{N} (2f\pot f\dep )\, \eq (\W\pot  - \W\dep )\,\e^{rt\frg}\w.
\end{equation}
%
The factor of $\eq$ describes the synapses being in the steady-state distribution before the memory is encoded. The factor of $(\M\pot-\M\dep)$ comes from the encoding of the memory at $t=0$, with $\wvi$ being $\pm1$ in synapses that are potentiated/depotentiated. The factor of $\e^{rt\frg}$ describes the subsequent evolution of the probability distribution, averaged over all sequences of plasticity events, and the factor of $\w$ indicates the readout via the synaptic weight.
